Manuscript

### 2015-02-09 inst/simulation/manuscript.Rmd
...

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[2]), subset(logMeanPopulationSizes, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), subset(logMeanPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png", width=8, height=4)

xlim <- log10(10^c(2,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), subset(logMeanPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[2]), subset(logMeanPopulationSizes2000, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), subset(logMeanPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png", width=8, height=4)

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), subset(logMeanPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[2]), subset(logMeanPopulationSizes10Days, modelName==modelNames[2]), modelName=modelNames[2], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), subset(logMeanPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c3.png", width=8, height=4)
```

@@

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp; 
logTable1

@@

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersections <- plyr::join(populationSizes, intersections)
intersections2000 <- plyr::join(populationSizes2000, intersections2000)
intersections10days <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersections, .(Scenario, modelName), i.stat)
ddply(intersections2000, .(Scenario, modelName), i.stat)
ddply(intersections10days, .(Scenario, modelName), i.stat)
```

@@

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=2)
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=c("T", "ST")) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames, panel="a", scenarioNames=scenarios)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames, panel="b", scenarioNames=scenarios)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames, panel="c", scenarioNames=scenarios)
cip <- rbind(cip1, cip2, cip3)
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)

>>>>

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[1]), subset(logMeanPopulationSizes, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[3]), subset(logMeanPopulationSizes, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes, modelName==modelNames[4]), subset(logMeanPopulationSizes, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3a3.png", width=8, height=4)

xlim <- log10(10^c(2,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[1]), subset(logMeanPopulationSizes2000, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[3]), subset(logMeanPopulationSizes2000, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes2000, modelName==modelNames[4]), subset(logMeanPopulationSizes2000, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3b3.png", width=8, height=4)

xlim <- log10(10^c(0,4)); ylim <- xlim
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[1]), subset(logMeanPopulationSizes10Days, modelName==modelNames[1]), modelName=modelNames[1], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c1.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[3]), subset(logMeanPopulationSizes10Days, modelName==modelNames[3]), modelName=modelNames[3], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c2.png", width=8, height=4)
p <- plotLogPopulationSize(subset(logPopulationSizes10Days, modelName==modelNames[4]), subset(logMeanPopulationSizes10Days, modelName==modelNames[4]), modelName=modelNames[4], xlim=xlim, ylim=ylim)
saveFigure(p, "manuscript-figure-3c3.png", width=8, height=4)
```

@@

table1 <- getPopulationSizesTable(populationSizes, meanPopulationSizes, overEstimate=2000)
logTable1 <- getPopulationSizesTable(logPopulationSizes, logMeanPopulationSizes, overEstimate=log10(2000+1))
logTable1$MeanProp <- table1$MeanProp; logTable1$SDProp <- table1$SDProp;

@@

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersections <- plyr::join(populationSizes, intersections)
intersections2000 <- plyr::join(populationSizes2000, intersections2000)
intersections10days <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(o.mean=mean(x$Observed), o.sd=sd(x$Observed), e.mean=mean(x$Estimated), e.sd=sd(x$Estimated),
                                 pp.mean=round(mean(x$Estimated/x$Observed), 2), pp.sd=round(sd(x$Estimated/x$Observed), 2),
                                 i.mean=mean(x$intersections), i.sd=sd(x$intersections), ip.mean=round(mean(x$intersections/x$Observed),2), ip.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersections, .(Scenario, modelName), i.stat)
ddply(intersections2000, .(Scenario, modelName), i.stat)
ddply(intersections10days, .(Scenario, modelName), i.stat)

@@

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=Inf)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) + scale_colour_manual("Model", values=c("darkgray", "black"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion within CI") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank())
  return(p)
}
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[1:3], panel="a", scenarioNames=scenarios)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1:3], panel="b", scenarioNames=scenarios)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1:3], panel="c", scenarioNames=scenarios)
cip <- subset(rbind(cip1, cip2, cip3), modelName != "SmoothModel-nbinomial-ar1")
p <- plotCIProportions(cip)
saveFigure(p, "manuscript-figure-5.png", width=6, height=2)
